Discovery of s-process stars in the LAMOST survey

### 2018-01-24 article/ms.tex
be gentle

It's important to highlight our research only discovered $<2$\,\% sodium presence in our 257 Barium candidates, contrary to previous studies \citep[e.g.][]{decastro2016}. Also, synonymous to our s-process candidates, synthesized sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star. And, in juxtaposition to the literature, our 5 sodium enhanced stars exhibit a surface gravity range between 2.98 and 3, showing no correlation between higher [Na/Fe] values and lower log g values. These considerations suggest sodium-rich material from the TP-AGB star polluted our 5 Barium candidates, but also, sodium enhancement is not unbiquitous in Barium Stars.

\subsection{Technetium enhancement}
Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star, enhancemnt in this element in our sample would indicate the presence of AGB stars \citep{jorissen1993}, and suggest some of our candidates are intrinsic Barium stars. Our analyse discovered 51 single Tc line matches within our 257 Barium star candidate sample. However, for Tc to be present in  a star the enhancement lines must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are data artifacts. In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic. It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.

@@

\subsection{Extrinsic and intrinsic Barium stars}
Barium stars exist as either intrinsic or extrinsic objects. Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previosuly polluting TP-AGB star companion. Figure \ref{fig:figure2} demonstrates the majority of our Barium star sample has a surface gravity greater then 2, highlighting that our sample is primarily not massive enough to have reach the TP-AGB phase and therefore, must be extrinsic Barium stars.

@@

Our research discovered 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST. This is the largest sample of s-process enhanced stars to date. Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium ehancement is not ubiquitous in s-process stars as previously claimed. We highlight that the majority of our Barium stars have a surface gravity greater then 2, this suggests that these are extrinsic Barium stars

@@

>>>>

It's important to highlight our research only discovered $<2$\,\% sodium presence in our 257 Barium candidates, contrary to previous studies \citep[e.g.][]{decastro2016}. This suggests systematic differences in the analyse undertaken by said previous studies. Also, synonymous to our s-process candidates, synthesized sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star. And, in juxtaposition to the literature, our 5 sodium enhanced stars exhibit a surface gravity range between 2.98 and 3, showing no correlation between higher [Na/Fe] values and lower log g values. These considerations suggest sodium-rich material from the TP-AGB star polluted our 5 Barium candidates, but also, sodium enhancement is not unbiquitous in Barium Stars.

\subsection{Technetium enhancement}
Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star. Enhancemnt in Tc would indicate the presence of AGB stars \citep{jorissen1993}, and suggest some of our candidates are intrinsic Barium stars. Our analyse discovered 51 single Tc line matches within our 257 Barium star candidate sample. However, for Tc to be present in  a star the enhancement lines must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are data artifacts. In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic. It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.

@@

\subsection{Extrinsic and intrinsic Barium stars}
Barium stars exist as either intrinsic or extrinsic objects. Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previosuly polluting TP-AGB star companion. Figure \ref{fig:figure2} demonstrates the majority of our Barium star sample has a surface gravity greater then 2, highlighting that our sample is primarily not massive enough to have reach the TP-AGB phase and therefore, must be extrinsic Barium stars. Furthermore, this suggests other enhancements including our 5 sodium and 178 carbon enhanced Barium stars exist through TP-AGB companion pollution.

@@

Our research discovered 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST. This is the largest sample of s-process enhanced stars to date. Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium ehancement is not ubiquitous in s-process stars as previously claimed. We highlight that the majority of our Barium stars have a surface gravity greater then 2, this suggests that these are extrinsic Barium stars.

@@

\bibitem[\protect\citeauthoryear{Casey}{2014}]{casey2014}
Casey, A.~R. 2014, 
PhDT, 394
\todo{format Andy's ref properly}
%@PHDTHESIS{2014PhDT.......394C,
%   author = {{Casey}, A.~R.},
%    title = "{A Tale of Tidal Tales in the Milky Way}",
% keywords = {Astronomy, Astrophysics, Stellar streams},
%   school = {Australian National University},
%     year = 2014,
%    month = May,
%      doi = {10.5281/zenodo.49493},
%   adsurl = {http://adsabs.harvard.edu/abs/2014PhDT.......394C},
%  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
%}
